Predictive analytics in quality assurance for assembly processes: lessons learned from a case study at an industry 4.0 demonstration cell

### 2021-06-15 02_Paper/paper.tex
Minor edits on corresponding author and table captions

\aucores{* Corresponding author. Tel.: +49-271-740-2630; fax: +49-271-740-12628. {\it E-mail address:} alejandro.perez@uni-siegen.de}

@@

With the evolution of machine learning (ML) applications \cite{bishop2006pattern}, approaches combining QC and predictive models are becoming more relevant. The applications range from the defect analysis of the produced piece \cite{Carlos2018MLforQC, Sohnius2019PASurfacequality}, to process-oriented QC \cite{krauss2020automated, krauss2019machine, aumi2012model, ritter1992neue}, see Section~\ref{sec:related_works}. 
Independently of the research area previously stated, within the scope of the related works, there is no evidence of an evaluation framework for diverse ML techniques applied in QC process.

@@

default hyperparameters, which we found to work well.
\footnote{To allow exact reproduction of our results source code

@@

       \caption{Confusion matrices result of the prediction of 50 test data-points. We present the result of the predictions given by all three algorithms in detail based on the comparison between true values vs predictions. The tables read from the upper-left cell as: true-positive, false-positive, false-negative, true-negative.}

@@

\vspace{0.1cm}
\footnotesize
\textbf{Author Contributions}
Pérez M. and Wolter writing - original draft, conceptualization, review, and editing; investigation; software and data curation.
Schmallenbach writing - review, editing.
Burggräf, Wagner, Heinbach, Steinberg writing - conceptualization, review. Garcke, and Steffes-lai writing - review.
% Burggräf performed supervision of work.

>>>>

\aucores{* Corresponding author. Tel.: +49-271-740-2630; fax: +49-271-740-12628. {\it E-mail address:} fabian.steinberg@uni-siegen.de}

@@

With the evolution of machine learning (ML) applications \cite{bishop2006pattern}, approaches combining QC and predictive models are becoming more relevant. The applications range from the defect analysis of the produced piece \cite{Carlos2018MLforQC, Sohnius2019PASurfacequality}, to process-oriented QC \cite{krauss2019machine, krauss2020automated,  aumi2012model, ritter1992neue}, see Section~\ref{sec:related_works}. 
Independently of the research area previously stated, within the scope of the related works, there is no evidence of an evaluation framework for diverse ML techniques applied in QC process.

@@

default hyperparameters, which we found to work well. \footnote{To allow exact reproduction of our results source code

@@

       \caption{Confusion matrices result of the prediction of 50 test data-points. }

@@

\vspace{0.1cm}
\footnotesize
\textbf{Author Contributions}
Pérez M. and Wolter writing - original draft, conceptualization, review, and editing; investigation; software and data curation.
Schmallenbach writing - review, editing.
Burggräf, Wagner, Heinbach, Steinberg writing - conceptualization, review. Garcke, and Steffes-lai writing - review.
